---
title: "Temperature-Dependent Functional Response Models"
author: "Andy Davidson"
date: "10/14/2020"
output: html_document
---

# FR Fits for Fall 2018 Temp-Dependent Functional Responses for Ae. Atropalpus Prey

```{r}
#Load in data
erdat <- read.csv( "ErSimp_FRData.csv" )
pddat <- read.csv( "PdLong_FRData.csv" )

require( emdbook )
require( bbmle )
require( R2WinBUGS )
require( plotrix )
require( plyr )
require( Hmisc )
require( broom )

source( "ModelingFunctions.R" )
```

All functional responses shown here are being fit with depletion, using the equation for Roger's Type II functional response. Data are log-transformed, as suggested by Uzsko et al. 2020 (Ecosphere).

There are several candidate models for the shape of the temperature-dependence of attack rate and handling time, but we'll be using the ones described by Sentis et al. 2012.

##First Predator: *Erythemis simplicicollis*

Now, we'll attempt to fit the functional response for Erythemis. The current fit uses a general value for Tl for Libellulids (42.2C, from Garten and Gentry 1976), and an estimate for T0 (10C; based on growth CTmin, Suhling et al. 2015):

```{r}
erdat$TempK <- erdat$Temp + 273.15
sv.log <- list( b = log( 1.105563e-01 ), h0 = log( 1.99775e-14 ), Eh = log( 0.65 ) )

frfit_ery <-
  mle2(
    Killed ~ dbinom( prob = (
      rogers.sentis.risk.log( N0, b, T0 = log( 283.15 ), Tl = log( 315.35 ), h0, M = 114.2, bh = 0.75, Eh, k = 8.62e-5, TempK, t = 1 )
    ),
    size = N0 ),
    start = sv.log,
    trace = TRUE,
    data = erdat
  )

summary( frfit_ery )
parms_ery <- tidy( frfit_ery )
```

##Second predator: *Pachydiplax longipennis*

We will follow the same exact procedure as above for the Pachydiplax fits. 

```{r}
pddat$TempK <- pddat$Temp + 273.15
sv.log <- list( b = log( 3.2e-02 ), h0 = log( 2.1e-07 ), Eh = log( 0.22 ) )

frfit_pachy <-
  mle2(
    Killed ~ dbinom( prob = (
      rogers.sentis.risk.log( N0, b, T0 = log( 283.15 ), Tl = log( 314.85 ), h0, M = 68.7, bh = 0.75, Eh, k = 8.62e-5, TempK, t = 1)
    ),
    size = N0 ),
    start = sv.log,
    trace = TRUE,
    data = pddat
  )

summary( frfit_pachy )
parms_pachy <- tidy( frfit_pachy )

# Clean up and write data to a file
predparms <- rbind( parms_ery, parms_pachy )
predspp <- c( "ErSimp", "ErSimp", "ErSimp", "PdLong", "PdLong", "PdLong" )
predparms[ "spp" ] <- predspp
predparms <- predparms[ c( "spp", "term", "estimate", "std.error" ) ]

write.csv( predparms, "Parms_PredFR.csv", row.names = FALSE )
```

