---
title: "Temperature-Dependent Prey Development Model"
author: "Andy Davidson"
date: "10/14/2020"
output: word_document
---

```{r}
require( bbmle )
require( lme4 )
require( broom )
require( nlstools )
require( propagate )

devdata <- read.csv( "ModelingFunctions.R" )
source( TDPred_Functions.R )
```

The following document contains code used to model the temperature-dependence of larval development and mortality rates for rock pool mosquitoes (<i>Aedes atropalpus</i>). 

```{r}
#Arrhenius-rate model:
sv <- list( c = 0.4, b = -1 )
arr.rate.model <-  nls(
  DevRate ~ arr.rate( c, b, Temp ),
  data = devdata,
  start = sv,
  trace = TRUE
)

#Arrhenius-time model:
sv <- list( c = 0.4, b = -1 )
arr.time.model <- nls(
  DevTime ~ arr.time( c, b, Temp ),
  data = devdata, 
  start = sv,
  trace = TRUE
)

#Save the parameters below for both fits:
parms_atro_rate <- tidy( arr.rate.model )
parms_atro_time <- tidy( arr.time.model )

parms_atro_rate$model <- c( "arr.rate" )
parms_atro_time$model <- c( "arr.time" )

write.csv( parms_atro_rate, "Parms_PreyDev.csv", row.names = FALSE )
```

Next, we'll fit a model describing temperature-dependent mortality rates for <i>Aedes atropalpus</i>. This is a little trickier, because there's a lot less precedent for it in the literature. Due to the shape of the data, I've decided to fit this as a logistic model, shown below.

```{r}
#First, we convert the survivorship data in the .csv to a daily rate:
devdata$MortalityRate <- ( ( 1 - devdata$Survivorship ) / devdata$DevTime )

#Then, we fit the model:
logisticcurve <- nls( MortalityRate ~ ( 1 / ( 1 + exp( -r * ( Temp - x1 ) ) ) + y1 ), start = list( x1 = 34, y1 = 0.015,r = 0.1), data = devdata, trace=TRUE )

summary( logisticcurve )

#This yields the following parameters:
parms_atromort <- tidy( logisticcurve )
write.csv( parms_atromort, "Parms_PreyMort.csv", row.names = FALSE )
```

